Verifying Demonstrations

### 2019-02-19 paper/adversary-model.tex
Minor edits to adversary model

This adversary represents an adversary that has no access to data from outside 
the system, \eg inferences that can be made from the communication layer (\eg 
IP-addresses mapped to physical identities or face recognition), which means 
that it has only the protocol data at its disposal.

>>>>

This adversary has no access to data from outside the system, \eg inferences 
that can be made from the communication layer (\eg IP-addresses mapped to 
physical identities or face recognition from the protest), which means that it 
has only the protocol data at its disposal.
